---
title: "Check transformation and overlaps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Check transformation and overlaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# Load libraries
library(readr)
suppressPackageStartupMessages(library(dplyr))
library(DT)
library(ggplot2)
library(linearpackcircles)

# Data
DF = read_csv("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/owid-covid-data.csv", show_col_types = FALSE) %>%
  filter(date == max(date)) # Keep only most recent data

```

## Original Plot

We filter the owid DB to show only one continent. The parameters `width_plot` and `height_group` can be adjusted to give enough space to the circles to move around. 

```{r createplot, fig.height=4, fig.width=16}

# Create Plot
linearpackcircles(DF %>% filter(continent == "Asia"),

                  ID_var = "location",
                  group_var = "continent",
                  area_var = "total_cases_per_million",
                  x_var = "total_deaths_per_million",

                  separation_factor = 1, # Separation between groups (i.e. continents)
                  width_plot = 250, # width "units"
                  height_group = 10, # height within each group

                  label_circles = TRUE,
                  max_overlaps = 8,
                  size_text = 2, 
                  
                  highlight_ID = "Armenia") +
  labs(title = "COVID deaths per million",
       x = "Deaths per million",
       caption = "Diameter is cases per million \n Data from https://github.com/owid/covid-19-data \nBy @gorkang")

```

If we don't give enough space, the circles will start to overlap, or the x axis displacement may be too much for our taste.  

```{r createplot2, fig.height=7, fig.width=16}

# Create Plot
linearpackcircles(DF %>% filter(continent == "Asia"),

                  ID_var = "location",
                  group_var = "continent",
                  area_var = "total_cases_per_million",
                  x_var = "total_deaths_per_million",

                  separation_factor = 1, # Separation between groups (i.e. continents)
                  width_plot = 50, # width "units"
                  height_group = 10, # height within each group

                  label_circles = TRUE,
                  max_overlaps = 8,
                  size_text = 2,
                  
                  highlight_ID = "Armenia") +
  labs(title = "COVID deaths per million",
       x = "Deaths per million",
       caption = "Diameter is cases per million \n Data from https://github.com/owid/covid-19-data \nBy @gorkang")

```

## Check

We can check both using the same parameters in the `check_linearpackcircles` function.  

```{r check_plot, fig.height=7, fig.width=16}

CHECKS = check_linearpackcircles(DF %>% filter(continent == "Asia"),

                  ID_var = "location",
                  group_var = "continent",
                  area_var = "total_cases_per_million",
                  x_var = "total_deaths_per_million",

                  separation_factor = 1, # Separation between groups (i.e. continents)
                  width_plot = 50, # width "units"
                  height_group = 10, # height within each group
                  CHECKS_plots = TRUE # Show overlaps plot
                  ) 

```

We can see a DF with the details of the overlaps.

```{r check_dfoverlaps, fig.height=7, fig.width=16}
datatable(CHECKS$DF_overlaps)
```

Show a plot highlighting where the overlaps are.

```{r check_plot_overlaps, fig.height=5, fig.width=16}
CHECKS$plots_overlaps
```

Overview of displacements.

```{r check_count_diffs, fig.height=7, fig.width=16}

datatable(CHECKS$DF_DIFFS[[1]]$count_output)

```

Detail of displacements

```{r check_diffs, fig.height=7, fig.width=16}

datatable(CHECKS$DF_DIFFS[[1]]$DF_output)

```
